Stable individual differences in strategies within, but not between, visual search tasks

### 2018-12-24 Manuscript/manuscript.tex
Fixed a couple of typos

Another example of differences in search strategy comes from the foraging literature \cite{kristjansson2014,johannesson2016}. In this context, foraging is a visual search task in which there are multiple targets on each trial. Participants were asked to search through a set of items from four categories, with two categories classed as targets. In the conjunction condition (searching for red-horizontal and green-vertical line segments among red-vertical and green-horizontal distracters), most observers searched in runs, finding all the targets of one target category, and then switching and finding the targets in the other category. This strategy has previously been observed in animal foraging \cite{dawkins1971}, and suggests holding one complex target template in mind at a time is a better strategy than switching templates. However, a sub-set of observers, termed `super-foragers', were able to change between search target categories with no cost to performance. This study has been run on touch displays\cite{kristjansson2014} (observers are asked to tap on as many targets as they can as quickly as possible) and a 3D computer game (in which participants navigate a squirrel through a virtual environment picking up targets with different feature combinations)[IN PREP], with super-foragers present in both versions. While test-retest reliability has not been measured explicitly for the foraging paradigm, the task was used as a measure to assess the effect of a six day long mindfulness retreat on cognitive performance\cite{hartkamp2017}. From a re-analysis of these data, we can estimate that the test-retest reliability for the mean run length is $r \approx 0.7$ for the feature condition and $r \approx 0.88$ for the conjunction search.

@@

\subsection{Participants}
64 students with normal or corrected-to-normal vision from the University of Aberdeen took part in this study\footnote{data from an additional 11 participants was discarded due to being recorded with an inappropriate screen resolution. Another participant was exluded due to colour blindness.}. Participants were compensated for their time with either  course credit or \pounds 15. All participants gave informed consent. The study was approved by the University of Aberdeen Psychology Ethics Committee.

@@

We view these findings, not as a disappointing null result, but as thought-provoking and exciting. Vogel and Awh\cite{vogel2008} argued that studying individual differences in cognitive psychology (in their case, working memory) provides valuable insight to containing potential theories of the underlying cognitive mechanisms. Our results suggest that context and structure of the task also needs to be taking into account and we hope that studying how an individual's behaviour varies across different search tasks will lead to the development of a more comprehensive theory of search.

>>>>

Another example of differences in search strategy comes from the foraging literature \cite{kristjansson2014,johannesson2016}. In this context, foraging is a visual search task in which there are multiple targets on each trial. Participants were asked to search through a set of items from four categories, with two categories classed as targets. In the conjunction condition (searching for red-horizontal and green-vertical line segments among red-vertical and green-horizontal distracters), most observers searched in runs, finding all the targets of one target category, and then switching and finding the targets in the other category. This strategy has previously been observed in animal foraging \cite{dawkins1971}, and suggests holding one complex target template in mind at a time is a better strategy than switching templates. However, a sub-set of observers, termed `super-foragers', were able to change between search target categories with no cost to performance. This study has been run on touch displays\cite{kristjansson2014} (observers are asked to tap on as many targets as they can as quickly as possible) and a 3D computer game (in which participants navigate a squirrel through a virtual environment picking up targets with different feature combinations)\cite{prpic2018}, with super-foragers present in both versions. While test-retest reliability has not been measured explicitly for the foraging paradigm, the task was used as a measure to assess the effect of a six day long mindfulness retreat on cognitive performance\cite{hartkamp2017}. From a re-analysis of these data, we can estimate that the test-retest reliability for the mean run length is $r \approx 0.7$ for the feature condition and $r \approx 0.88$ for the conjunction search.

@@

\subsection{Participants}
64 students with normal or corrected-to-normal vision from the University of Aberdeen took part in this study\footnote{data from an additional 11 participants was discarded due to being recorded with an inappropriate screen resolution. Another participant was excluded due to colour blindness.}. Participants were compensated for their time with either  course credit or \pounds 15. All participants gave informed consent. The study was approved by the University of Aberdeen Psychology Ethics Committee.

@@

We view these findings, not as a disappointing null result, but as thought-provoking and exciting. Vogel and Awh\cite{vogel2008} argued that studying individual differences in cognitive psychology (in their case, working memory) provides valuable insight to containing potential theories of the underlying cognitive mechanisms. Our results suggest that context and structure of the task also needs to be taken into account and we hope that studying how an individual's behaviour varies across different search tasks will lead to the development of a more comprehensive theory of search.
